CF Registry Analysis

### 2022-12-27 Christine Chan/CF Registry/cf_registry_analysis.qmd
fixed incidence denominator

```{r}
#| label: tbl-incidence_cffpr
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR Alone"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>%  
    filter(reviewyear==year,is.na(first_cfrd_cffpr) | first_cfrd_cffpr == year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>% 
    select(eDWID,`Age Group`,cfrd_cffpr)
  inc = inc %>% group_by(cfrd_cffpr) %>% count(`Age Group`,.drop = F)
  inc = inc[!is.na(inc$`Age Group`),]
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_cffpr=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

@@

```{r}
#| label: tbl-incidence_both
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR and OGTT"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,is.na(first_cfrd_both) | first_cfrd_both == year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>%
    select(eDWID,reviewyear,encounternum,`Age Group`,
           twohour_bloodglucose,cfrd_both,first_cfrd_both)
  inc = inc %>% group_by(cfrd_both) %>% count(`Age Group`,.drop = F)
  inc = inc[!is.na(inc$`Age Group`),]
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_both=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

>>>>

```{r}
#| label: tbl-incidence_cffpr
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR Alone"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>%  
    filter(reviewyear==year,is.na(first_cfrd_cffpr) | first_cfrd_cffpr >= year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>% 
    select(eDWID,`Age Group`,cfrd_cffpr)
  inc = inc %>% group_by(cfrd_cffpr) %>% count(`Age Group`,.drop = F)
  inc = inc[!is.na(inc$`Age Group`),]
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_cffpr=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)

@@

```{r}
#| label: tbl-incidence_both
#| tbl-cap: "Year-on-Year Incidence of CFRD Based on CFFPR and OGTT"
# For each year, pull everyone with and without CFRD that year
year_inc = function(df=encounter,year,py = 1000){
  # Filter and count
  inc = df %>% 
    filter(reviewyear==year,is.na(first_cfrd_both) | first_cfrd_both >= year) %>%
    group_by(eDWID) %>% filter(row_number() == 1) %>%
    select(eDWID,reviewyear,encounternum,`Age Group`,
           twohour_bloodglucose,cfrd_both,first_cfrd_both)
  inc = inc %>% group_by(cfrd_both) %>% count(`Age Group`,.drop = F)
  inc = inc[!is.na(inc$`Age Group`),]
  # Calculations
  new_cases = sum(inc$n[inc$cfrd_both=="Yes"])
  total_at_risk = sum(inc$n)
  total_inc = new_cases/(total_at_risk/py)
